\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-27 paper.tex
Proof read part 1

The components which make use of spatial and temporal models of the environment
are usually found in the intermediate layers of robotic architectures, between
the low-level perceptual layers, and the high-level decisional layers. They
include modules like geometric reasoners (that compute spatial and topological
relations between objects), motion planners, action recognition.

These different components typically exhibit different needs in terms of model,
like different nominal spatial and/or temporal resolutions. For instance, a 3D
motion planner would typically use coarse 3D models of surrounding objects to
lower the computational load while planning, while a module assessing the
visibility of objects might need on the contrary a high-resolution model of the
environment for accurate 3D rendering. This requirement of multiple
task-specific representations has been framed as the need for \emph{deep
representation} by Beetz~\cite{beetz2010towards}.

@@

Traditional robotic middlewares like ROS are not particularly well-suited to
deal with these different needs: full geometric data can be represented, but are not
first-class citizens (for instance, basic tasks like displaying a 3D mesh at a dynamic
position are not particularly easy with ROS) and critically, representing and reasoning
on alternative models of the environment is not directly feasible.

Representing \emph{alternative states} is however often highly desirable. For instance,
software components manipulating environment models typically perform better if
the models are physically consistent. However, low-level perception inaccuracies
often introduce hard-to-avoid physical inconsistencies (like
detected objects floating in the air, or on the contrary wrongly inset into
other objects). Therefore, a post-process stage (for instance, using a physics
simulation engine) might be needed to displace the objects seen
by the robot into physically-correct positions. Implemented with a classical
approach (for instance, using ROS TF frames), we would get an object {\tt book}
located at the frame {\tt book\_frame}, and a secondary frame {\tt
book\_frame\_corrected} computed by the physics engine. It is easy to see why
such an approach would be quickly confusing (where is in fact my book?) and would not
scale well, with the robot's 3D model cluttered with spurious frames.

Another relevant example pertains to geometric task planning: a geometric task
planner typically need to reason over hypothetical future states of the
environment (``what happen if I move this glass onto that pile of books?'').
The planner might want to quickly generate possible future states, that
themselves might require further processing (for instance, running a physics
simulation). This use-case evidences the need for a flexible representation
system, where models are derived from each others, with partial modifications
and different timescales.

A third example relates to human-robot interaction scenarios where \emph{perspective
taking} is important (a prototypical example being the game `I spy with my
little eyes', as implemented in~\cite{ros2010which}). Perspective taking is a
cognitive skill that relies on the ability for an agent to project itself in
others' `eyes' to estimate what they see from their perspective. While
perspective taking has been previously implemented in robotics by temporary placing
virtual cameras at eyes position for each of the humans tracked by the
robot~\cite{ros2010solving}. a the face of  swapping the different viewpoints
to compute visibility is not directly possible

Geometric \emph{pre-supposition accommodation} makes another interesting case
for alternative worlds representation. \emph{Pre-supposition accommodation}
comes originally from linguistics, where it describes the mechanism by which
\emph{context is adjusted [...] to accept [...] a sentence that imposes certain
requirements on the context in which it is
processed}~\cite{vonfintel2008presupposition}. In the context of spatio-temporal
representations, we call pre-supposition accommodation the ability for an agent
to adjust its model so that it matches some external contextual constraint. For
instance, if A tells B to ``catch the red balloon behind you'', B adds a
representation of a red balloon behind him, even without actually seeing the
balloon: B accommodates the pre-supposition of a red balloon being present
behind himself. Endowing robots with this capability has been touched by
Mavridis \etal within their multi-modal \emph{Grounded Situation
Model}~\cite{Mavridis2006}. However, to the best of our knowledge, a general
framework which would enable robots to derive imaginary worlds by extending of
modifying existing ones has not been proposed so far.

The main contribution of this work is a generic approach to represent and share
\textbf{multiple parallel representations of the world}. \uwds does so by
permitting clients to clone an existing world, modify it, and re-share it,
without the cost of duplicating geometric data (as explained in
section~\ref{design}). By organizing clients in a network
(Figure~\ref{fig|scene}), worlds can be made dependent on each other, resulting
in a loosely-coupled modular approach to spatio-temporal world representation
that we call \emph{cascading situation assessment}.

>>>>

The components which make use of spatial and temporal models of the environment
are usually found in the intermediate layers of robotic architectures, between
the low-level perceptual layers, and the high-level decisional layers. They
include modules like geometric reasoners (that compute spatial and topological
relations between objects), motion planners or action recognition modules.

These components exhibit different needs in terms of model,
like different nominal spatial and/or temporal resolutions. For instance, a 3D
motion planner would typically use coarse 3D models of surrounding objects to
lower the computational load while planning, while a module assessing the
visibility of objects might need on the contrary  high-resolution models 
for accurate 3D rendering. This requirement of multiple
task-specific representations has been framed as the need for \emph{deep
representations} by Beetz~\cite{beetz2010towards}.

@@

Traditional robotic middlewares like ROS are not particularly well-suited to
deal with these different needs: full geometric data can be represented, but are
not first-class citizens (basic tasks like displaying a 3D mesh at a dynamic
position are not particularly easy to perform with ROS) and critically,
representing and reasoning on alternative states of the environment is not
directly feasible.

Representing alternative states is however often highly desirable. For instance,
software components manipulating environment models typically perform better if
the models are physically consistent. However, low-level perception inaccuracies
often introduce hard-to-avoid physical inconsistencies (like detected objects
floating in the air, or on the contrary wrongly inset into other objects).
Therefore, a post-process stage (for instance, using a physics simulation
engine) is needed to displace the objects seen by the robot into
physically-correct positions. Implemented with a classical approach (for
instance, using ROS TF frames), we would represent an object {\tt book} with two
frames: the original frame (\eg {\tt book\_frame\_raw}) and a second one
computed by the physics engine (\eg {\tt book\_frame\_corrected}). Such an
approach leads to the robot's 3D model being cluttered with multiple frames and
does not scale well.

Another example pertains to geometric task planning: a geometric task planner
typically needs to reason over hypothetical future states of the environment
(``what happen if I move this glass onto that pile of books?'').  The planner
generates many possible future states, that themselves might require further
processing (for instance, running a physics simulation). Such a tool would
benefit a flexible representation system, where models are derived from each
others, with partial modifications and different timescales.

A third example relates to human-robot interaction scenarios where \emph{perspective
taking} is important (a prototypical example being the game `I spy with my
little eyes', as implemented in~\cite{ros2010which}). Perspective taking is a
cognitive skill that relies on the ability for an agent to project itself in
others' `eyes' to estimate what they see from their perspectives. 
Perspective taking has been previously implemented in robotics by temporary placing
virtual cameras at eyes position for each of the humans tracked by the
robot~\cite{ros2010solving}. While acceptable for simple cases, such an approach
does not permit to maintain truly independent models of the environment for each
agent, and in particular does not permit false-beliefs
modelling~\cite{lemaignan2015mutual} whereas separate, independent world models
would effectively support such a skill.

Lastly, geometric \emph{pre-supposition accommodation} makes another interesting
case for alternative worlds representation. \emph{Pre-supposition accommodation}
comes originally from linguistics, where it describes the mechanism by which
\emph{context is adjusted [...] to accept [...] a sentence that imposes certain
requirements on the context in which it is
processed}~\cite{vonfintel2008presupposition}. In the context of spatio-temporal
representations, we call pre-supposition accommodation the ability for an agent
to adjust its model so that it matches some contextual constraint. For instance,
if A tells B to ``catch the red balloon behind you'', B might create a
representation of an imaginary red balloon, placed behind him, even without
actually observing the balloon: B \emph{accommodates} the \emph{pre-supposition}
of a red balloon being present behind himself. Endowing robots with this
capability has been touched by Mavridis \etal within their multi-modal
\emph{Grounded Situation Model}~\cite{Mavridis2006}. However, to the best of our
knowledge, a general framework which would enable robots to accommodate spatial
and temporal pre-suppositions by deriving imaginary worlds from existing ones
has not been proposed so far.

\uwds addresses this need and the main contribution of this work is a generic
approach to \textbf{represent and share multiple parallel representations of the
world}. \uwds does so by permitting clients to clone existing worlds, modify
them, and re-share them, without the cost of duplicating geometric data (as
explained in section~\ref{design}). By organizing clients in a network
(Figure~\ref{fig|scene}), worlds can be made dependent on each other, resulting
in a loosely-coupled modular approach to spatio-temporal world representation
that we call \emph{cascading situation assessment}.
